---
title: "Anime Data by MyAnimeList.net"
author: "Omar Rosas Bringas"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
editor_options:
  chunk_output_type: inline
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, message = FALSE, warning = FALSE)
```

```{r set-up, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggtext)
library(ggrepel)
library(patchwork)

# ggplot theme
source("../DataFeast_utilities/DataFeast_theme.R")
```

## Data

There is already a dataset related to anime in a tidy format that can be found [here](https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-04-23/tidy_anime.csv). However, this dataset is not updated and we know that the anime is something that can change between seasons and there are new animes each time.

With that in mind, we write and use a Python script to practice the **web scrapping** in the [My Anime List](https://myanimelist.net/). Here we only focus in the **Horror** Genre as it is the most near to the **Gore** Genre that is no present in this website.

```{r}
df_horror <- read_csv("WebScrapping/dataset_anime_Horror.csv")
head(df_horror)
```

## Data Preparation

This dataset contain diferent variables  that can be useful to explore. But before we need to prepare some columns.

We need to preare the columns `ranked` and `popularity` in which we only want to left the number. Meanwhile, in the column `links` we want to left only the **anime name** and the **anime ID** that will be used in case `Title English` is not correct and if there is a duplicate we can use this ID as will be unique.

```{r}
df_corrected <- df_horror %>% 
  mutate(
    ranked = str_replace(ranked, "Ranked #", ""),
    popularity = str_replace(popularity, "Popularity #", ""),
    links = str_replace(links, "https://myanimelist.net/anime/", ""),
    ranked = as.numeric(ranked),
    popularity = as.numeric(popularity),
    scored_by = as.numeric(scored_by),
    score = as.numeric(score)
    ) %>% 
  separate(col = links, into = c("ID_Anime", "Anime_name"), sep = "/") %>% 
  mutate(Anime_name = str_replace_all(Anime_name, "_", " "))
head(df_corrected)
```

## Data Visuzalition

### Studio counts

First we want to show how many or which **Anime Studies** has more animes with the **Horror** Genre.

```{r data-studio}
df_gore_studio <- df_corrected %>% 
  group_by(Studio) %>% 
  summarise(unique_titles = n_distinct(ID_Anime)) %>% 
  filter(unique_titles > 5, Studio != "-") %>% 
  ungroup() %>% 
  mutate(Studio = fct_reorder(Studio, unique_titles)) %>% 
  na.omit(Studio) %>% 
  arrange(desc(unique_titles))
```

We know that to represent this we can use a **Barplot** however we want to change a little the design and make a **Lollipop Chart** as we have more levels. Also we are interested in add our own logo from DATA FEAST

```{r gore-loliplot}
img_mad <- png::readPNG("img/Mad_House.png")
img_mad <- grid::rasterGrob(img_mad, interpolate = TRUE)

gore_loliplot <- ggplot(df_gore_studio, aes(x = Studio, y = unique_titles)) +
  geom_segment(aes(x = Studio, y = 0, xend = Studio, yend = unique_titles), 
               color = "#b0c9d5", linetype = "twodash", size = 0.8, alpha = 0.9) +
  geom_point(color = redBright, size = 8, alpha = 0.9) +
  geom_text(aes(label = unique_titles), color = "black", size = 10,stat = "unique") +
  coord_flip(clip = "off") +
  scale_y_continuous(limits = c(0,50), expand = c(0.01,0)) +
  guides(fill = "none") +
  labs(x = "Anime Studios", y = "Count Horror Animes",
       caption = "Visualization: <b style='font-family:Norsebold;font-size:20pt'>DATA FEAST</b> | Picture credit: Studio MAD HOUSE") +
  # annotation_custom(feast, xmin=-0.5, xmax=-1.5, ymin=-5, ymax=-20) +
  annotation_custom(img_mad, xmin = 0.8, xmax = 9.75, ymin = 15, ymax = 45) +
  theme(axis.text.x = element_text(family = "Lato", size = 30),
        axis.text.y = element_text(family = "Lato", size = 30),
        plot.margin = unit(c(1, 1, 1, 1), "lines"))

ggsave(plot = gore_loliplot, paste0(Sys.Date(),"FeastViz_Studios_Horror.png"), dpi = 300)
```

## Scores

Now we want to explore the  this means the scores, how many people scored and number of ratings. Also it is posible to explore other variables, for example, know if the popularity is by specific source.

```{r horror-unique}
df_horror_group <- df_corrected %>% 
  group_by(ID_Anime) %>% 
  summarize_all(first) %>% 
  mutate(title = paste0(Title_japanese, "\n", Anime_name))
```

```{r horror-scores}
img_alucard <- png::readPNG("img/Hellsing.png")
img_alucard <- grid::rasterGrob(img_alucard, interpolate = TRUE)

gore_scores <- df_horror_group %>% 
  ggplot(aes(x = score, y = scored_by)) +
  geom_point(aes(size = members), color = wheat, alpha = 0.6) +
  geom_text_repel(data = filter(df_horror_group, scored_by > 3.0e05), 
                  aes(label = Anime_name), size = 10, 
                  #family = "noto", 
                  color = redBright,
                  segment.size = 0.6, xlim = c(3.5, 8.5), box.padding = 0.5, force = 2,) +
  scale_x_continuous(limits = c(2,11)) +
  scale_y_continuous(labels = scales::comma,
                     limits = c(0,1.5e6),expand = c(0.01, 0.01)) +
  scale_size_continuous( name = "Times listed by MAL users:",
                         breaks = c(1000, 10000, 100000, 250000, 500000),
                         labels = c("  1,000", " 10,000", "100,000", "250,000", "500,000")) +
  guides(size = guide_legend(override.aes = list(alpha = 1))) +
  labs( x = "Average user score", y = "Number of ratings", 
        caption = "Visualization: <b style='font-family:Norsebold;font-size:20pt'>DATA FEAST</b>| Picture credit: Hellsing") +
  annotation_custom(img_alucard, xmin = 8.0, xmax = 12, ymin=550000, ymax = 1550000) +
  theme(axis.text = element_text(family = "Lato"),
        legend.position = c(0.15,0.5),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_text(size = 32),
        legend.text = element_text(family = "Lato", size = 30))
ggsave(plot = gore_scores, paste0(Sys.Date(),"FeastViz_AnimeScores_Horror.png"), dpi = 300, width = 10)
```

Instead of using the size variable with members we can explore by `source` this means to know where the anime cames, if is based on manga, novel or anything else. But to explore better this we need to make less levels otherwise we would have many and couldn't see them in a easy way.

```{r horror-source}
df_horror_group <- df_horror_group %>% 
  mutate(Source_class = case_when(
    Anime_source %in% c('Manga', 'Visual novel', 'Web manga') ~ 'Manga',
    Anime_source %in% c('Novel', 'Light novel', 'Book') ~ 'Novel',
    Anime_source %in% c('Game') ~ 'Game',
    Anime_source %in% c('Original') ~ 'Original',
    Anime_source %in% c('Other', 'Unknown', 'Picture book', 'Music') ~ 'Others')
  )
```

```{r horror-source-plot}
img_another <- png::readPNG("img/another_per.png")
img_another <- grid::rasterGrob(img_another, interpolate = TRUE)

colors_source <- c("Manga" = "#e8e3e2", "Game" = "#006ead", "Original" = "#ffda86",
                   "Novel" = "#dd003e", "Others" = "#5ac624")

gore_scores_bysource <- df_horror_group %>% 
  ggplot(aes(x = score, y = scored_by)) +
  geom_point(aes(color = Source_class), alpha = 0.3) +
  geom_text_repel(data = filter(df_horror_group, scored_by > 0.9e05 & Source_class == "Novel"), 
                  aes(label = Anime_name), size = 12,
                  #family = "Lato",
                  color = waterRal,
                  segment.size = 0.4, xlim = c(4.0, 9.0), box.padding = 0.9, force = 5) +
  scale_x_continuous(limits = c(4,9)) +
  scale_y_continuous(labels = scales::comma,
                     limits = c(0,1.5e6), expand = c(0.01, 0.01)) +
  scale_color_manual(values = colors_source) +
  guides(color = guide_legend(title = "Anime Source", override.aes = list(alpha = 1), ncol = 2)) +
  labs( x = "Average user score", y = "Number of ratings", 
        caption = "Visualization: <b style='font-family:Norsebold;font-size:20pt'>DATA FEAST</b> | Picture credit: Another") +
  annotation_custom(img_another, xmin = 4.1, xmax = 7.3, ymin= 10000, ymax = 2400000) +
  theme(axis.text = element_text(family = "Lato"),
        legend.position = c(0.20,0.40),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_text(size = 35, hjust = 0.5, color = greyLight),
        legend.text = element_text(family = "Lato", size = 30))

ggsave(plot = gore_scores_bysource, paste0(Sys.Date(),"FeastViz_Horror_Source.png"), dpi = 300)
```

And finally, we are interested in **Berserk** (RIP Kentaro Miura) which unfortunately the anime adaptations have not very well scored. Also we can see the anime's type..

```{r berserk}
img_guts <- png::readPNG("img/Berserk.png")
img_guts <- grid::rasterGrob(img_guts, interpolate = TRUE)

colors_type <- c("Movie"="#00b0a2",
                 "TV" = "#e8ff00", 
                 # "OVA" = "#ff8ba6",
                 # "Music" = "#6096f2",
                 "Special" = "#35e400"
                 # "ONA" = "#c5d9ea"
                 )

gore_scores_berserk <- df_horror_group %>% 
  ggplot(aes(x = score, y = scored_by)) +
  geom_point(data = filter(df_horror_group, !str_detect(Anime_name, "Berserk")), alpha = 0.3, color = greyMetal) +
  geom_point(data = filter(df_horror_group, str_detect(Anime_name, "Berserk")), aes(color = Type), alpha = 0.9) +
  geom_text_repel(data = filter(df_horror_group, str_detect(Anime_name, "Berserk")), 
                  aes(label = Anime_name), size = 11,
                  #family = "Lato",
                  color = redBright,
                  segment.size = 0.6, xlim = c(5.5, 10.0), box.padding = 0.8, force = 5, nudge_y = 1e4) +
  scale_x_continuous(limits = c(3,9.5)) +
  scale_y_continuous(labels = scales::comma,
                     limits = c(0,1.5e6), expand = c(0.01, 0.01)) +
  scale_color_manual(values = colors_type) +
  guides(color = guide_legend(title = "Type", override.aes = list(alpha = 1), ncol = 1)) +
  labs( x = "Average user score", y = "Number of ratings", 
        caption = "Visualization: <b style='font-family:Norsebold;font-size:20pt'>DATA FEAST</b> | Picture credit: Berserk") +
  annotation_custom(img_guts, xmin = 2.5, xmax = 5.5, ymin=1.4e5, ymax = 1.5e6) +
  theme(axis.text = element_text(family = "Lato"),
        legend.position = c(0.50,0.85),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_text(size = 35, hjust = 0.5, color = greyLight, face = "bold"),
        legend.text = element_text(family = "Lato", size = 30, face = "bold"))
ggsave(plot = gore_scores_berserk, paste0(Sys.Date(),"FeastViz_AnimeScores_Horror_Berserk.png"), dpi = 300, width = 10)
```

Finally, what we can do is know the animes by studio and see who has more ratings and present in a jitter plot.

```{r}
df_horror_group <- df_horror_group %>% 
  mutate(Studio = case_when(
    Studio %in% c("Studio Pierrot,             Pierrot Plus", "Studio Pierrot,             Pierrot Plus") ~ "Studio Pierrot",
    Studio == "Madhouse,             Satelight,             Graphinica" ~ "Madhouse",
    Studio == "Millepensee,             GEMBA" ~ "Millepensee",
    TRUE ~ Studio
  ))
```


```{r horror_anime_studios}
gore_studios_score <- df_horror_group %>% 
  filter(score > 6 & scored_by > 100000)  %>% 
  mutate(Studio = fct_reorder(Studio, score)) %>% 
  ggplot(aes(x = Studio, y = scored_by)) +
  geom_jitter(color = wheat, show.legend = FALSE, size = 3, width = 0.1) +
  geom_text_repel(data = df_horror_group %>%
                    filter(score > 6 & scored_by > 100000) %>%
                    group_by(Studio) %>% 
                    slice_max(order_by = scored_by, n = 1),
                  aes(label = Anime_name), size = 11, 
                  #family = "Lato",
                  color = greyMetal,
                  segment.size = 0.3, box.padding = 0.2, force = 5, nudge_y = 1e5) +
  labs(x= "Anime Studios", y = "Number of ratings", 
       caption = "Visualization: <b style='font-family:Norsebold;font-size:20pt'>DATA FEAST</b>", 
       title = "Best Horror Animes by Studio") +
  guides(fill = "none") +
  # coord_flip(clip = "off") +
  scale_y_continuous(labels = scales::comma,
                     limits = c(0, 1.5e6)) +
  theme(axis.text = element_text(family = "Lato"),
        axis.text.x = element_text(angle = 45, hjust = 1))
ggsave(plot = gore_studios_score, paste0(Sys.Date(),"FeastViz_AnimeScores_Horror_studios.png"), dpi = 300, width = 15)
```

```{r fullpanel}
## fullpanel
infogra <- (gore_loliplot | gore_scores_bysource | gore_scores_berserk) /
  gore_studios_score + plot_annotation(title = "Horror Animes ratings in 2021", theme = 
                                         theme(plot.title = element_text(size =100, face= "bold", hjust = 0.5)))

ggsave(plot = infogra, paste0(Sys.Date(),"FeastViz_animesHorror.png"), dpi = 300, width = 22, height = 15)
```

### Shojo

One last thing that we want to do is make a cool design from the dataset of Shojo Anime and as one of the favorites is **Sakura CardCaptor** we also have a dataset from the studios that make the anime which is **MadHouse**.

The process to preparing the data will be the same with the addition of separate the **Genres**.

```{r}
df_madhouse <- read_csv("WebScrapping/dataset_anime_Madhouse.csv")
df_madhouse <- df_madhouse %>% 
  mutate(
    ranked = str_replace(ranked, "Ranked #", ""),
    popularity = str_replace(popularity, "Popularity #", ""),
    links = str_replace(links, "https://myanimelist.net/anime/", ""),
    ranked = as.numeric(ranked),
    popularity = as.numeric(popularity),
    scored_by = as.numeric(scored_by),
    score = as.numeric(score)
    ) %>% 
  separate(col = links, into = c("ID_Anime", "Anime_name"), sep = "/") %>% 
  mutate(Anime_name = str_replace_all(Anime_name, "_", " ")) %>% 
  separate_rows(Genres, sep = ";")
head(df_madhouse)
```

```{r}
library(RColorBrewer)

font_add("Sakura", "../DataFeast_utilities/garton.normal.ttf")
showtext_auto()
sakura_colors <- c("#e9ebe7",
                   "#f0e1d8",
                   "#ba7176",
                   "#c4957a",
                   "#dfd3c3",
                   "#e4d0a5",
                   "#efb57a",
                   "#EBBCB0")
sakura <- colorRampPalette(colors = sakura_colors)

img_mad <- png::readPNG("img/Mad_House.png")
img_mad <- grid::rasterGrob(img_mad, interpolate = TRUE)

img_sak <- png::readPNG("img/Sakura_1.png")
img_sak <- grid::rasterGrob(img_sak, interpolate = TRUE)
```

```{r}
madhouse <- df_madhouse %>% 
  group_by(Genres) %>% 
  count() %>% 
  filter(n > 45) %>% 
  ungroup() %>% 
  mutate(Genres = fct_reorder(Genres, n)) %>% 
  ggplot(aes(x = Genres, y = n)) +
    geom_col(aes(fill = Genres), color = "#ab9560", size = 1.5) +
    coord_flip() +
    scale_y_continuous(limits = c(0, 150), expand = c(0.01, 0)) +
    scale_fill_manual(values = sakura(9)) +
    guides(fill = "none") +
    labs(x ="Most Common Genres", y = "Count") +
    annotation_custom(img_mad, xmin = 0.5, xmax = 2.75, ymin = 75, ymax = 145) +
    annotation_custom(img_sak, xmin = 2.25, xmax = 5.25, ymin = 80, ymax = 150) +
    theme(
      text = element_text(color = "#9f2148", family = "Sakura", face = "bold"),
      panel.border = element_rect(size = 0.75),
      plot.background = element_rect(color = "#dedfcf", fill = "#dedfcf"),
      legend.background = element_rect(colour = NA, fill = "#dedfcf"),
      legend.key = element_rect(color = "#dedfcf", fill = "#dedfcf"),
      legend.box.background = element_blank(),
      legend.position = c(0.2,0.25),
      legend.text = element_text(family = "Lato", size = 20),
      legend.title = element_text(family = "Lato", size = 25),
      axis.text = element_text(color = "#9f2148", size = 50),
      axis.title.x = element_text(size = 75),
      axis.title.y = element_text(size = 75),
      plot.caption = element_markdown(size = 25, 
                                      hjust = 1, vjust = 0, margin = margin(t = 10), colour = "#001b1e", family = "Lato")
    )
ggsave(plot = madhouse, "Sakura_Studio.png", dpi = 300)
```

```{r}
df_madhouse_unique <- df_madhouse %>% 
  group_by(ID_Anime) %>% 
  summarize_all(first)
head(df_madhouse_unique)
```

```{r}
img_sak <- png::readPNG("img/Sakura_2.png")
img_sak <- grid::rasterGrob(img_sak, interpolate = TRUE)
```


```{r}
plot_scores<- df_madhouse_unique %>% 
  ggplot(aes(x = score, y = scored_by)) +
  geom_point(aes(size = members), color = "#9f2148", alpha = 0.35) +
  geom_text_repel(data = df_madhouse_unique %>% filter(scored_by > 5e5 | str_detect(Title_english, "Cardcaptor Sakura")),
                  aes(label = Anime_name),
                  force = 5, box.padding = 0.5, xlim = c(7,10.0), color = "#21cbfb", size = 12, family = "Lato") +
  guides(size = guide_legend(override.aes = list(alpha = 1.0))) +
  labs(x = "Average MAL User Score", y = "Number Of Ratings",
       caption = "Visualization: <b style='font-family:Norsebold;font-size:35pt'>DATA FEAST</b> | Picture: Sakura CardCaptor"
       ) +
  # Scales 
  scale_y_continuous(expand = c(0.01, 0.01), limits = c(0, 2.1e6), labels = scales::comma) +
  scale_x_continuous(limits = c(5,10)) +
  scale_size_continuous(name = "Times listed by MAL users:",
                          breaks = c(1000, 10000, 100000, 250000, 1000000), 
                          labels = c("  1,000", " 10,000", "100,000", "250,000", "1,000,000")) +
  annotation_custom(img_sak, xmin = 4.0, xmax = 8.0, ymin = 0.9e6, ymax = 2.1e6) +
  coord_cartesian(clip = "off") +
  theme(
      text = element_text(color = "#9f2148", family = "Sakura", face = "bold"),
      panel.border = element_rect(size = 0.75),
      plot.background = element_rect(color = "#dedfcf", fill = "#dedfcf"),
      legend.background = element_rect(colour = NA, fill = "#dedfcf"),
      legend.key = element_rect(color = "#dedfcf", fill = "#dedfcf"),
      legend.box.background = element_blank(),
      legend.position = c(0.2,0.25),
      legend.text = element_text(family = "Lato", size = 20),
      legend.title = element_text(family = "Lato", size = 25),
      axis.text = element_text(color = "#9f2148", size = 50),
      axis.title.x = element_text(size = 75),
      axis.title.y = element_text(size = 75),
      plot.caption = element_markdown(size = 25, 
                                      hjust = 1, vjust = 0, margin = margin(t = 10), colour = "#001b1e", family = "Lato")
    )
ggsave(plot = plot_scores, "Sakura_ratings.png", dpi = 300)
```

```{r}
sakura_mad <- madhouse + plot_scores + 
  plot_annotation(title = "Sakura CardCaptor's Anime Studio", theme = 
                                         theme(
                                           plot.background = element_rect(color = "#dedfcf", fill = "#dedfcf"),
                                           plot.title = element_text(size =135, face= "bold", 
                                                                     hjust = 0.5, family = "Sakura", color = "#9f2148")))

ggsave(plot = sakura_mad, paste0(Sys.Date(),"FeastViz_animeSakura.png"), dpi = 300, width = 15, height = 7)
```










